Refactoring `nls()`: a constructive critique

### 2023-02-03 RefactoringNLS/JNAB230203.Rmd
Strategic issues in selfStart

>>>>

### Strategic issues in `selfStart` models

By providing starting values that are likely to be reasonable and by including 
Jacobian code in the `selfStart` model code, some of the deficiencies of the 
Gauss-Newton algorithm are mitigated. However, creating such functions is a lot 
of work, and their
documentation (file `./src/library/stats/man/selfStart.Rd`) is quite complicated.
We believe that the focus should be placed on getting good initial parameters,
that is `getInitial()` function, though avoiding the current calls back to `nls()`.
Interactive tools, such as "visual fitting" (@nash1996nonlinear) might be
worth considering.

We also note that the introduction of `scaleOffset` in R 4.1.1 to deal with the 
convergence test for small residual problems now requires that the `getInitial()`
function have dot-arguments (`...`) in its argument list. This illustrates the
entanglement of many features in `nls()`.
